That-s-a-BigAss-Chicken

### 2025-02-28 Manuscript_Final.qmd
bibliography stuff

---
title: "That-s-a-BigAss-Chicken"
shorttitle: "Example apaquarto manuscript"
author:
  - name: W. Joel Schneider
    corresponding: true
    orcid: 0000-0002-8393-5316
    email: schneider@temple.edu
    affiliations:
      - name: Temple University
        department: College of Education and Human Development
        address: 1301 Cecil B. Moore Ave.
        city: Philadelphia
        region: PA
        postal-code: 19122-6091
    role:
      - writing
      - conceptualization
  - name: Fulano Zutano Mengano
    affiliations: Universidad de Dondequiera
    orcid: 0000-0000-0000-0001
    role:
      - formal anlaysis
      - visualization
      - editin
  - name: Thomas Richard Harris
    affiliations: 
      - name: Generic State University
        department: Department of Scholarly Studies
    orcid: 0000-0000-0000-0002
    role:
      - editing
      - funding acquistion
  - name: Wut C. Whosis
    affiliations: Whatchama College
    orcid: 0000-0000-0000-0003
    role:
      - software
      - methodology
      - editing
- name: Natalie Dowling
corresponding: true
orcid: 0000-0002-7190-1979
email: ndowling@uchicago.edu
affiliations:
- name: University of Chicago
department: Master of Arts Program in the Social Sciences
address: 5801 S. Ellis Ave.
city: Chicago
region: IL
postal-code: 60637
abstract: "This and fi l e shows the basic format for a Quarto notebook using the
'apaquarto' extension, which provides a template for APA style manuscripts. The
YAML header includes some properties that will be commonly used, but there are
many more options. The body of the notebook includes markdown text and code
chunks, and references can be included using a BibTeX file. When the document is
rendered, the output will be rendered in APA style."
keywords: [quarto, tutorials, R language]
a u t h o r - n o t e :
d i s c l o s u r e s :
conflict of interest: The author has no conflict of interest to declare.
references. bib # create a b i b file in the root directory of your
project
f o r m a t :
#apaquarto-docx: default # you can render your project in html, doc, and/or pdf
apaquarto-html: default
comment out some as you're working and don't need them
format: pdf
---

```{r}
setwd("/Users/kristenjohnson/KristenWorkingDirectory/That-s-a-BigAss-Chicken/temp")
quarto::quarto_use_template("wjschne/apaquarto", no_prompt
= TRUE)
```

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

>>>>

---
title: "That-s-a-BigAss-Chicken"
shorttitle: "Example apaquarto manuscript"
author:

- name: Natalie Dowling
corresponding: true
orcid: 0000-0002-7190-1979
email: ndowling@uchicago.edu
affiliations:
- name: University of Chicago
department: Master of Arts Program in the Social Sciences
address: 5801 S. Ellis Ave.
city: Chicago
region: IL
postal-code: 60637
abstract: "This and fi l e shows the basic format for a Quarto notebook using the
'apaquarto' extension, which provides a template for APA style manuscripts. The
YAML header includes some properties that will be commonly used, but there are
many more options. The body of the notebook includes markdown text and code
chunks, and references can be included using a BibTeX file. When the document is
rendered, the output will be rendered in APA style."
keywords: [quarto, tutorials, R language]
author-note:
  disclosures:
    conflict of interest: The author has no conflict of interest to declare.
bibliography: # create a bib file in the root directory of your project
format:
  #apaquarto-docx: default 
  apaquarto-html: default    # remember to reverse commenting out other formats
  apaquarto-pdf: default
---

```{r}

```

Chickens are pretty great [@elkhoraibiBackyardChickensUnited2014; @fischerDefenceBackyardChickens2019; @schindlerBackyardChickensFrontYard].

/clear
# References
